Forecasting hourly hospital admission

### 2021-10-07 paper/paper.Rmd

---
title:  Forecasting hourly hospital admission
author:
  - name: Author1
    email: email1@example.com
    affiliation: University1
    footnote: 1
  - name: Author2
    email: email2@example.com
    affiliation: University2
    footnote: 2
  - name: Ivan Svetunkov
    email: i.svetunkov@lancaster.ac.uk
    affiliation: Centre for Marketing Analytics and Forecasting, Lancaster University, UK
    footnote: 2
address:
  - code: University1
    address: Cardiff business school, 3 Colum Drive, CF10 3EU, Cardiff
  - code: University2
    address: adress2
  - code: University3
    address: adress3
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"

@@

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggridges)
library(hrbrthemes)
library(ggthemes)
library(scales)
library(ggtext)
library(extrafont)
```

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('../r_script/data-viz.R')
knitr::read_chunk('../r_script/admision_viz.R')
```

@@

```{r fig-quantilebias, fig.cap= "Quantile ...", fig.align='center',out.width= "90%"}
knitr::include_graphics(rep("../results/QuantileBias.png"))
```

@@

```{r fig-skill, fig.cap= "Skill score ...", fig.align='center',out.width= "90%"}
knitr::include_graphics(rep("../results/Skill_rel2bench_reduced.png"))
```

>>>>

---
title:  Forecasting hourly hospital admission
author:
  - name: Author1
    email: email1@example.com
    affiliation: University1
    footnote: 1
  - name: Jethro Browell
    email: jethro.browell@glasgow.ac.uk
    affiliation: School of Mathematics and Statistics, University of Glasgow, UK
    footnote: 2
  - name: Ivan Svetunkov
    email: i.svetunkov@lancaster.ac.uk
    affiliation: Centre for Marketing Analytics and Forecasting, Lancaster University, UK
    footnote: 2
address:
  - code: University1
    address: Cardiff business school, 3 Colum Drive, CF10 3EU, Cardiff
  - code: University2
    address: adress2
  - code: University3
    address: adress3
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"

@@

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, fig.pos = 'H', message = FALSE, warning = FALSE)
# Make sure you have the latest versions of rmarkdown and rticle
library(tidyverse)
library(lubridate)
library(bookdown)
library(patchwork)
library(tsibble)
library(kableExtra)
library(ggplot2)
library(data.table)
library(RColorBrewer)
library(ggridges)
library(hrbrthemes)
library(ggthemes)
library(scales)
library(ggtext)
library(extrafont)
```

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('../r_script/data-viz.R')
knitr::read_chunk('../r_script/admision_viz.R')
knitr::read_chunk('../r_script/result_viz.R')
```

@@

```{r fig-quantilebias, fig.cap= "Quantile ...", fig.align='center',out.width= "90%"}
#knitr::include_graphics(rep("../results/QuantileBias.png"))
## Should reduce the number of models shown here... it's really hard to tell them appart!

REL_nom <- data.table(Nominal=seq(0,1,by=0.05),
                      Empirical=seq(0,1,by=0.05),
                      `Quantile Bias`= 0,
                      Method="Nominal")

REL[,`Quantile Bias`:=Empirical-Nominal]

ggplot(data=REL[Horizon=="All" & Issue == "All",],aes(x=Nominal,y=`Quantile Bias`,group=Method,color=Method)) +
  geom_line(data=REL_nom,aes(x=Nominal,y=`Quantile Bias`), color="black",size=1.1,show.legend = F) +
  geom_line() + geom_point() +
  xlim(c(0,1)) + ylim(c(-0.2,0.2)) + #ggtitle("Quantile Bias") +
  theme_few() 
```

@@

```{r fig-skill, fig.cap= "Skill score ...", fig.align='center',out.width= "90%"}
knitr::include_graphics(rep("../results/Skill_rel2bench_reduced.png"))

# knitr::include_graphics(rep("../results/Skill_rel2bench_reduced.png"))

load("../results/all_results_paper_2021-10-07.Rda")

plotdata <- melt(bootdata[,100*(get(REF)-.SD)/get(REF),.SDcols=NAMES],
                 measure.vars =  1:length(NAMES),variable.name = "Method",
                 value.name = "Skill Score")

## Merge Reliability for colouring...
plotdata <- merge(plotdata,REL[kfold=="Test" & Horizon=="All" & Issue == "All",.(Qbias=mean(abs(Nominal-Empirical))),by="Method"],
                  by="Method",all.x = T)

ggplot(plotdata[`Skill Score`>-2,], aes(x=reorder(Method, -`Skill Score`), y=`Skill Score`, fill=Qbias)) + 
  ylab("Pinball Skill Score [%]") +
  geom_boxplot() + theme_few() +
  # ggtitle("Pinball Skill Score Relative to Benchmark 2") +
  theme(axis.text.x = element_text(angle = -80)) + #scale_fill_manual(values=cbPalette) +
  # scale_x_discrete(labels= paste0(substring(NAMES, 1,4),".")) +
  geom_hline(yintercept=0, linetype="dashed",size=0.5)+
  scale_fill_gradientn(colours = rev(brewer.pal(n = 11, name = "RdYlGn")),
                       limits=c(0,0.11))+
  labs(fill = "Quantile Bias",x="Method")
